{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-20 documents/experiment_1_data.tex
edits

\begin{center}
	\begin{tabular}{ |c|c|c| } 
		\hline
		 & col2 & col3 \\
		\hline
		\multirow{3}{4em}{Multiple row} 
		& cell2 & cell3 \\ 
		& cell5 & cell6 \\ 
		& cell8 & cell9 \\ 
		\hline
	\end{tabular}
\end{center}

>>>>

\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c| } 
		\hline
		Exposure & kilocounts per 10s integration & Note \# \\
		\hline
		Autoclaved phage & 30 & \\ 
		Autoclaved p. (50 uL) & 32 & Run 8\\ 
		\hline
		Phage culture 'blank' & 8 & \\ 
		Dist. water & 0.5 \\
		\hline
		\multicolumn{3}{|c|}{\ntilde 10 or 20 us  } \\
		\hline
		 & \\ 
		\hline
		\multicolumn{3}{|c|}{\ntilde 10 or 20 us, pH 10.6} \\
		\hline
		\multicolumn{3}{|c|}{\ntilde 0.2 mm \ntilde 0.25 MV/m, 0.2 uL/s, various pulse counts  } \\
		\hline 
		 Blank & 8 & Li test 1\\
		 + & 8 & Li test 1\\
 		 + & 7 & Li test 1\\
 		 + & 7 & Li test 1\\
 		 \hline
		\multicolumn{3}{|c|}{\ntilde 0.05 mm \ntilde 1 MV/m, 0.2 uL/s, various pulse counts  } \\
		\hline
		Sham & 5 & Sma. co. \\
		+ & 6 & Sma. co.  \\ 
		+ & 6 & Sma. co.  \\ 
		\hline
	\end{tabular}
\end{table}

Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts per 10 seconds. thoroughly characterized.

Field strengths are very approximate.

Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.

Repeatability between test conditions was not terrific. The source of the \ntilde 5000 count variation between some equivalent samples is not known. However, in no case did any tube approach the 22 to 30 kcounts of the autoclave.

Stock culture had titer $3\times 10^9$ T4r.

The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.

Results aggregated over the course of several months.

In all cases, thermal artifact was completely di

The firmware and data analysis scripts originally randomly generated blinded sham and autoclave assignments and automatically treated the samples accordingly. It also printed blinded templates for pipetting. This was done partly in the hopes that massively oversampling the microwave absorption spectrometer across the physical tolerances would highlight any resonances and changes in the resonances.

However, as the spectrometer was abandoned, this non-deterministic property caused significant issues while troubleshooting the fluorescence detection system, and \st{expedience} \textit{laziness} prompted us to disable this system. This violates best practices.

A layer of silicone conformal coating was applied to the 0.2 mm

### 2021-02-20 documents/summary.tex
edits

Nephelometry (right-angle light scattering measurement) and turbidimetric (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E. coli cultures do not .  Turbidimetry Impedimietric In addition, removing the necessitating 
$\beta$-galactosidase luciferase Promega Beta-Glo\cite{rapid2014}. While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo assaying compared unfavorably to direct fluorescence for this application, but this may have been user error.

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\centering
	\subfloat[Direct electron beam detection]{
		\includegraphics[width=0.3\textwidth]{direct_electron_beam}
	}
	\subfloat[Damage to the sensor, believed to be due to. ]{
		\includegraphics[width=0.3\textwidth]{e_beam_damage_2}

	}
	\subfloat[]{
		\includegraphics[width=0.3\textwidth]{e_beam_damage}

	}

	\caption{Second.}
	\hfill

@@

>>>>

Nephelometry (right-angle light scattering measurement) and turbidimetric (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E. coli cultures do not .  Turbidimetry Impedimietric In addition, removing the necessitating 
E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for metabolism. luciferase Promega Beta-Glo\cite{rapid2014}. However, the one part contains a proprietary detergent to lyse cells.

While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when two components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo compared unfavorably to direct fluorescence for this application.

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\centering
	\subfloat[Direct electron beam detection]{
		\includegraphics[width=0.3\textwidth]{direct_electron_beam}
	}
	\subfloat[Damage to the sensor, believed to be due to. ]{
		\includegraphics[width=0.3\textwidth]{e_beam_damage_2}
	}
	\subfloat[]{
		\includegraphics[width=0.3\textwidth]{e_beam_damage}
	}
	\caption{Second.}
	\hfill

@@

Thanks to Oughston and Sarris for information on dispersion;
